Smart Drill-Down

### 2015-07-16 TableSummarization/Paper/intro.tex
added stuff from tech report
changes

In this paper, we present a new interaction operator 
that is an extension to a traditional 
drill down operator, aimed at providing {\em complementary}
functionality to drill down in cases where drill down is
ineffective. We call our operator {\em smart drill down}.
At a high level, smart drill down lets analysts zoom into
the more ``interesting'' parts of a table or a database,
with fewer operations, and without having to examine as much
data as traditional drill down.
Note that our goal is {\em not} to replace traditional 
drill down functionality, which we believe is fundamental;
instead, our goal is to provide auxiliary functionality 
which analysts are free to use whenever they find 
traditional drill downs ineffective.

@@

Incidentally, note that in the example we only described one type of smart drill down,
where the analyst selects a {\em rule} to drill down on
(e.g., the Walmart rule going from Table~\ref{table:introexample} to
Table~\ref{table:introexample2}.
In Section~\ref{sec:interface} we describe another option
where the analyst clicks on a $\star$ in a column to obtain
rules that have non-$\star$ values in that column.

Our work on smart drill down is related
to table summarization and anomaly
detection~\cite{Sarawagi:2001:UMA:767141.767148,
Sarawagi00user-adaptiveexploration,
Sarawagi98discovery-drivenexploration,
DBLP:journals/pvldb/GebalyAGKS14}.
These papers mostly focus on
giving the most ``surprising'' information to the user, i.e., information
that would minimize the Kullback-Liebler(KL) divergence between the
resulting maximum entropy distribution and the actual value distribution. For instance, if a certain set of
values occur together in an unexpectedly small number of tuples, that
set of values may be displayed to the user. In contrast, our algorithm
focuses on rules with high counts, covering as
much of the table as possible.
Furthermore, our summarization is couched in
an interactive environment, where the analyst
directs the drill down and can tailor the optimization criteria.
Nevertheless, one can envision extending traditional
and smart drill down to provide an additional option of anomaly detection. 
\mrjdel{We discuss related work in detail in  Section~\ref{sec:related}.}

\mrj{Our work is also related to pattern mining. Several pattern mining papers~\cite{Vreeken:2011:KMI:1969593.1969615,Bringmann:2007:ICDM,Yan:2005:SIP:1081870.1081907} focus on providing one shot summaries of data, but do not propose interactive mechanisms. Moreover, to the best of our knowledge, other pattern mining work is either not flexible enough~\cite{Goethals:2011:MFI:2020408.2020529,Tatti:2014:FRI:2676651.2656261,DeBie:2010:FMI:1816112.1816117}, restricting the amount of tuning the user can perform, or so general~\cite{Leeuwen:2012:DSS:2347179.2347243} as to preclude efficient optimization. Our work also merges `interesting pattern mining' into the OLAP framework. We discuss related work in detail in Section~\ref{sec:related}.}

>>>>

In this paper, we present a new interaction operator 
that is an extension to the traditional 
drill down operator, aimed at providing {\em complementary}
functionality to drill down in cases where drill down is
ineffective. We call our operator {\em smart drill down}.
At a high level, smart drill down lets analysts zoom into
the more ``interesting'' parts of a table or a database,
with fewer operations, and without having to examine as much
data as traditional drill down.
Note that our goal is {\em not} to replace traditional 
drill down functionality, which we believe is fundamental;
instead, our goal is to provide auxiliary functionality 
which analysts are free to use whenever they find 
traditional drill downs ineffective.

@@

Incidentally, note that in the example we only described one type of smart drill down,
where the analyst selects a {\em rule} to drill down on
(e.g., the Walmart rule going from Table~\ref{table:introexample} to
Table~\ref{table:introexample2}).
In Section~\ref{sec:interface} we describe another option
where the analyst clicks on a $\star$ in a column to obtain
rules that have non-$\star$ values in that column.

Our work on smart drill down is related
to table summarization and anomaly
detection~\cite{Sarawagi:2001:UMA:767141.767148,
Sarawagi00user-adaptiveexploration,
Sarawagi98discovery-drivenexploration,
DBLP:journals/pvldb/GebalyAGKS14}.
These papers mostly focus on
giving the most ``surprising'' information to the user, i.e., information
that would minimize the Kullback-Liebler(KL) divergence between the
resulting maximum entropy distribution and the actual value distribution. For instance, if a certain set of
values occur together in an unexpectedly small number of tuples, that
set of values may be displayed to the user. In contrast, our algorithm
focuses on rules with high counts, covering as
much of the table as possible.
Furthermore, our summarization is couched in
an interactive environment, where the analyst
directs the drill down and can tailor the optimization criteria.
Nevertheless, one can envision extending traditional
and smart drill down to provide an additional option of anomaly detection.

Our work is also related to pattern mining. Several pattern mining papers~\cite{Vreeken:2011:KMI:1969593.1969615,Bringmann:2007:ICDM,Yan:2005:SIP:1081870.1081907} focus on providing one shot summaries of data, but do not propose interactive mechanisms. Moreover, to the best of our knowledge, other pattern mining work is either not flexible enough~\cite{Goethals:2011:MFI:2020408.2020529,Tatti:2014:FRI:2676651.2656261,DeBie:2010:FMI:1816112.1816117}, restricting the amount of tuning the user can perform, or so general~\cite{Leeuwen:2012:DSS:2347179.2347243} as to preclude efficient optimization. Our work also merges `interesting pattern mining' into the OLAP framework. We discuss related work in detail in Section~\ref{sec:related}.
